---
title: "Reysha Marie S. Salinas IT2C  LAB Exercise 1"
output:
  html_document: default
date: "2024-02-08"
---


200 PRODUCTS
```{r}

#Web Scraping for amazon
library(rvest)
library(dplyr)
library(polite)
library(stringr) 
library(httr)

url <- "https://www.amazon.com/s?i=computers-intl-ship&bbn=16225007011&rh=n%3A16225007011%2Cn%3A172456%2Cp_n_sb_certificate_id%3A98614993011&dc&ds=v1%3ASTq7Fh3bj0QuQYjUes0MMO4pO6Wsn2OnsK3Jws%2BuJOc&qid=1708962779&rnid=98614992011&ref=sr_nr_p_n_sb_certificate_id_1"

session <- bow(url, user_agent = "Educational Purposes")
session


 session1 <- session ("https://www.amazon.com/s?i=computers-intl-ship&bbn=16225007011&rh=n%3A16225007011%2Cn%3A172456%2Cp_n_sb_certificate_id%3A98614993011&dc&ds=v1%3ASTq7Fh3bj0QuQYjUes0MMO4pO6Wsn2OnsK3Jws%2BuJOc&qid=1708962779&rnid=98614992011&ref=sr_nr_p_n_sb_certificate_id_1")

name <- session1 %>%
  html_nodes("h2") %>%
  html_text()

one<- name[1:50]
one

price <- session1 %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price <- str_extract(price[1:50], "\\$[0-9.]+")
# Print or use the first price
print(first_price)


rating <- session1 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three<- rating[1:50]
three

review <- session1 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four<- review[1:50]
four

frame1 <- data.frame(
  Name = one, 
  Price = first_price, 
  Rating = three, 
  Reviews = four
)
frame1

url2 <- "https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk"

session2 <- bow(url2, user_agent = "Educational Purposes")
session2


session2 <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk") 


name2 <- session2 %>%
  html_nodes("h2") %>%
  html_text()

one2<- name2[1:48]
one2

price2 <- session2 %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price2 <- str_extract(price2[1:48], "\\$[0-9.]+")

# 
print(first_price2)


rating2 <- session2 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three2<- rating2[1:48]
three2

review2 <- session2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four2<- review2[1:48]
four2

frame2 <- data.frame(
  Name = one2, 
  Price = first_price2, 
  Rating = three2, 
  Reviews = four2
)
frame2

url3 <- "https://www.amazon.com.au/s?k=Computers%2C+Components+%26+Accessories&i=electronics&rh=n%3A4885077051&page=4&c=ts&qid=1708949256&ts_id=4885077051&ref=sr_pg_4"


session3 <- bow(url3, user_agent = "Educational Purposes")
session3


library(rvest)
library(stringr)
library(httr2)
library(httr) 


session3 <- session("https://www.amazon.com.au/s?k=Computers%2C+Components+%26+Accessories&i=electronics&rh=n%3A4885077051&page=4&c=ts&qid=1708949256&ts_id=4885077051&ref=sr_pg_4")


name3 <- session3 %>%
  html_nodes("h2") %>%
  html_text()

one3<- name3[1:24]
one3

price3 <- session3 %>%
  html_nodes("span.a-price") %>%
  html_text()

# 
first_price3 <- str_extract(price3[1:24], "\\$[0-9.]+")

# 
print(first_price3)


rating3 <- session3 %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three3<- rating3[1:24]
three3

review3 <- session3 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four3<- review3[1:24]
four3

frame3 <- data.frame(
  Name = one3, 
  Price = first_price3, 
  Rating = three3, 
  Reviews = four3
)
frame3


#Web Scraping for amazon
library(rvest)
library(dplyr)
library(polite)
library(stringr) 
library(httr)



url1p <- "https://www.amazon.com.au/b?node=4885077051&ref=lp_4851800051_nr_n_2"

session <- bow(url1p, user_agent = "Educational Purposes")
session

session1p <- scrape(session)
session1p

name1 <- session1p %>%
  html_nodes("h2") %>%
  html_text()

one1<- name1[1:24]
one1

price1 <- session1p %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price1 <- str_extract(price1[1:24], "\\$[0-9.]+")
# Print or use the first price
print(first_price1)


rating1<- session1p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three1<- rating1[1:24]
three1

review1 <- session1p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four1<- review1[1:24]
four1

frame11 <- data.frame(
  Name = one1, 
  Price = first_price1, 
  Rating = three1, 
  Reviews = four1
)
frame11


url2p <- "https://www.amazon.com.au/s?k=Computers%2C+Components+%26+Accessories&i=electronics&rh=n%3A4885077051&page=2&c=ts&qid=1708948457&ts_id=4885077051&ref=sr_pg_2" 

session1 <- bow(url2p, user_agent = "Educational Purposes")
session1

session2pt <- scrape(session1)
session2pt



name2p <- session2pt %>%
  html_nodes("h2") %>%
  html_text()

one2p<- name2p[1:24]
one2p

price2p <- session2p %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price2p <- str_extract(price2p[1:24], "\\$[0-9.]+")

# 
print(first_price2p)


rating2p <- session2p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three2p<- rating2p[1:24]
three2p

review2p <- session2p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four2p<- review2p[1:24]
four2p

frame2p <- data.frame(
  Name = one2p, 
  Price = first_price2p, 
  Rating = three2p, 
  Reviews = four2p
)
frame2p

url3p <- "https://www.amazon.com.au/s?k=Computers%2C+Components+%26+Accessories&i=electronics&rh=n%3A4885077051&page=3&c=ts&qid=1708948958&ts_id=4885077051&ref=sr_pg_3"

session3 <- bow(url3p, user_agent = "Educational Purposes")
session3


session3p <- scrape(session3)
session3p

name3p<- session3p %>%
  html_nodes("h2") %>%
  html_text()

one3p<- name3p[1:30]
one3p

price3p <- session3p %>%
  html_nodes("span.a-price") %>%
  html_text()

# 
first_price3p <- str_extract(price3p[30], "\\$[0-9.]+")

# 
print(first_price3p)


rating3p <- session3p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three3p<- rating3p[1:30]
three3p

review3p <- session3p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four3p<- review3p[1:30]
four3p

frame3p <- data.frame(
  Name = one3p, 
  Price = first_price3p, 
  Rating = three3p, 
  Reviews = four3p
)
frame3p
```
BIND
```{r}
products12<- bind_rows(frame1, frame2, frame3,frame11, frame2p, frame3p)
products12


```
CSV
```{r}
write.csv(products12,file = "ProductsReview200.csv")
```


Get the 25 Reviews each for 10 product. 
FIRST PRODUCT
```{r}
#product1 
library(rvest)
#product url 1

url1A <- "https://www.amazon.com.au/product-reviews/B0BHSS55RM/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session1 <-bow(url1A, user_agent = "Educational Purposes")
sessiont1A <- scrape(session1)

# name of reviewer
namerev1A <- sessiont1A %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer1A <- namerev1A[1:25] 
namer1A

# date of review
date1A <- sessiont1A %>%
  html_nodes("span.review-date") %>%
  html_text()

daterev1A <- date1A[1:25]
daterev1A
# individual rating
rateindi1A <- sessiont1A %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi1A <- rateindi1A[1:25]

# Review comment
revcom1A <- sessiont1A %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi1A <- revcom1A[1:25]
revi1A <- gsub("\n", "", revi1A)

framet1 <- data.frame(
  Name = namer1A, 
  Date = daterev1A, 
  IndividualRating = indi1A, 
  Review = revi1A
)
framet1


write.csv(framet1, file = "ReviewPRODUCT1.csv")
```
SECOND--------------------------
```{r}
#product2

library(rvest)

urlA <- "https://www.amazon.com.au/product-reviews/B0BTG4S29L/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

session12<-bow(urlA, user_agent = "Educational Purposes")
sessiontA <- scrape(session12)

# name of reviewer
namerevA <- sessiontA %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerA <- namerevA[1:25]
namerA
# date of review
dateA <- sessiontA %>%
  html_nodes("span.review-date") %>%
  html_text()

daterevA <- dateA[1:25]

# individual rating
rateindiA <- sessiontA %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiA <- rateindiA[1:25]
indiA
# Review comment
revcomA <- sessiontA %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviA <- revcomA[1:25]
reviA <- gsub("\n", "", reviA)

frametA <- data.frame(
  Name = namerA, 
  Date = daterevA, 
  IndividualRating = indiA, 
  Review = reviA
)
frametA
write.csv(frametA, file = "ReviewPRODUCT2.csv")

```
THIRD----
```{r}

urlB <- "https://www.amazon.com.au/product-reviews/B086WCG4SR/ref=p13n_ds_purchase_sim_1p_dp_desktop_d_sccl_1_2_cr/358-8254970-8794523?pd_rd_w=1SxUI&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=VX1KZQGA39ET6N51N4EP&pd_rd_wg=gaSN9&pd_rd_r=e92d4990-3f8e-486c-aebc-96f58ad50280&pd_rd_i=B086WCG4SR"

thirdproduct <- "https://www.amazon.com.au/product-reviews/B086WCG4SR/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=1SxUI&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=VX1KZQGA39ET6N51N4EP&pd_rd_wg=gaSN9&pd_rd_r=e92d4990-3f8e-486c-aebc-96f58ad50280&pd_rd_i=B086WCG4SR&pageNumber=1&sortBy=recent"

session1 <-bow(urlB, user_agent = "Educational Purposes")
sessiontB <- scrape(session1)

#2ndpart thrid product
session13 <-bow(thirdproduct, user_agent = "Educational Purposes")
sessiontB3 <- scrape(session13)

#name of reviewr

namerevB <- sessiontB %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerB<- namerevB[1:15]
namerB

#date of review
dateB <- sessiontB %>%
  html_nodes("span.review-date") %>%
  html_text()
dateB
daterevB<- dateB[1:15]

daterevB


#individual rating
rateindiB <- sessiontB %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiB<- rateindiB[1:15]
indiB


#Review comment 
revcomB <- sessiontB %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviB<- revcomB[1:15]
reviB<- gsub("\n", "", reviB)
reviB

framet2 <- data.frame(
  Name = namerB, 
  Date = daterevB, 
  IndividualRating = indiB, 
  Review = reviB
)
framet2

#2nd part 
#name of reviewr

namerevB3 <- sessiontB3 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerB3<- namerevB3[1:10]
namerB3

#date of review
dateB3 <- sessiontB3 %>%
  html_nodes("span.review-date") %>%
  html_text()
dateB3
daterevB3<- dateB3[1:10]

daterevB3


#individual rating
rateindiB3 <- sessiontB3 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiB3<- rateindiB3[1:10]
indiB3


#Review comment 
revcomB3 <- sessiontB3 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviB3<- revcomB3[1:10]
reviB3<- gsub("\n", "", reviB3)
reviB3

framet23 <- data.frame(
  Name = namerB3, 
  Date = daterevB3, 
  IndividualRating = indiB3, 
  Review = reviB3
)
framet23

framet23_ <- bind_rows(framet2,framet23)
framet23_
write.csv(framet23_, file = "ReviewPRODUCT3.csv")
```
FOURTH
```{r}
library(rvest)
library(dplyr)
library(httr2)
library(httr)
library(purrr)


product4 <- "https://www.amazon.com.au/product-reviews/B09TDTJKF1/ref=cm_cr_arp_d_viewopt_srt?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=1#reviews-filter-bar"
product4_1 <-"https://www.amazon.com.au/product-reviews/B09TDTJKF1/ref=cm_cr_getr_d_paging_btm_next_2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&sortBy=recent&pageNumber=2#reviews-filter-bar"

sessiontC <- bow(product4, user_agent = "Educational Purposes")
sessiontc <- scrape(sessiontC)
sessiontc
#second part /10 reviews
sessiontC2 <- bow(product4_1, user_agent = "Educational Purposes")
sessiontc2 <- scrape(sessiontC2)
sessiontc2

#name of reviewer
namerevC <- sessiontc %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerC <- namerevC[1:12]

#date of review
dateC <- sessiontc %>%
  html_nodes("span.review-date") %>%
  html_text()

daterevC <- dateC[1:12]

#individual rating
rateindiC <- sessiontc %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiC <- rateindiC[1:12]

#Review comment 
revcomC <- sessiontc %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviC <- revcomC[1:12]
reviC <- gsub("\n", "", reviC)

framet4 <- data.frame(
  Name = namerC, 
  Date = daterevC, 
  IndividualRating = indiC, 
  Review = reviC
)
framet4
# second part /10 reviews
namerevC2 <- sessiontc2 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerC2 <- namerevC2[1:13]

#date of review
dateC2 <- sessiontc2 %>%
  html_nodes("span.review-date") %>%
  html_text()

daterevC2 <- dateC2[1:13]

#individual rating
rateindiC2 <- sessiontc2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiC2 <- rateindiC2[1:13]

#Review comment 
revcomC2 <- sessiontc2 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviC2 <- revcomC2[1:13]
reviC2 <- gsub("\n", "", reviC2)

framet42 <- data.frame(
  Name = namerC2, 
  Date = daterevC2, 
  IndividualRating = indiC2, 
  Review = reviC2
)
framet42
framet4_ <- bind_rows(framet4,framet42)
framet4_

write.csv(framet4_, file = "ReviewPRODUCT4.csv")

```
FIFTH
```{r}
#product1 

product5 <- "https://www.amazon.com/product-reviews/B0C7GYX6MH/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"
product5_2 <- "https://www.amazon.com/product-reviews/B0C7GYX6MH/ref=acr_search_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

sessiontd <- bow(product5, user_agent = "Educational Purposes")
sessiontd
#part two/13 reviews
sessiontd2 <- bow(product5_2, user_agent = "Educational Purposes")
sessiontd2
library(rvest)
library(stringr)
library(httr2)
library(httr) 

sessiond <- scrape(sessiontd)
sessiond
sessiond2<- scrape(sessiontd2)
sessiond2


#part two/13 reviews

namerevD2 <- sessiond2 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerD2<- namerevD2[1:12]
namerD2

#date of review
dateD2<- sessiond2 %>%
  html_nodes("span.review-date") %>%
  html_text()
dateD2
daterevD2<- dateD2[1:12]
daterevD2


#individual rating
rateindiD2 <- sessiond2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiD2<- rateindiD2[1:12]
indiD2


#Review comment 
revcomD2 <- sessiond2 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviD2<- revcomD2[1:12]
reviD2 <- gsub("\n", "", reviD2)
reviD2

framet52 <- data.frame(
  Name = namerD2, 
  Date = daterevD2, 
  IndividualRating = indiD2, 
  Review = reviD2
)
framet52

#name of reviewr

namerevD <- sessiond %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerD<- namerevD[1:13]
namerD

#date of review
dateD <- sessiond %>%
  html_nodes("span.review-date") %>%
  html_text()
dateD
daterevD <- dateD[1:13]
daterevD


#individual rating
rateindiD <- sessiond %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiD<- rateindiD[1:13]
indiD


#Review comment 
revcomD <- sessiond %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviD<- revcomD[1:13]
reviD <- gsub("\n", "", reviD)
reviD

framet5 <- data.frame(
  Name = namerD, 
  Date = daterevD, 
  IndividualRating = indiD, 
  Review = reviD
)
framet5

framet5_ <- bind_rows(framet5,framet52)
framet5_

write.csv(framet5_, file = "ReviewPRODUCT5.csv")
```
SIXTH
```{r}
#product1 
library(polite)
product6 <- "https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=1"


#product6 
#Part one 13 reviews

sessiont <- bow(product6, user_agent = "Educational Purposes")
sessiont


sessiont <- session("https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=1")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:13]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:13]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:13]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:13]
revi <- gsub("\n", "", revi)
revi

framet <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet
#product 12 reviews

#Part two 12 reviews

product6_2 <- "https://www.amazon.com.au/product-reviews/B0BC2C71H1/ref=cm_cr_getr_d_paging_btm_next_3/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B0BC2C71H1&reviewerType=avp_only_reviews&pageNumber=3"

sessiont2 <- bow(product6_2, user_agent = "Educational Purposes")
sessiont2


sessiontF1 <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful")

#name of reviewr

namerevF1 <- sessiontF1 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerF1<- namerevF1[1:12]
namerF1

#date of review
dateF1 <- sessiontF1 %>%
  html_nodes("span.review-date") %>%
  html_text()
dateF1
daterevF1 <- dateF1[1:12]
daterevF1


#individual rating
rateindiF1 <- sessiontF1 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiF1<- rateindiF1[1:12]
indiF1


#Review comment 
revcomF1 <- sessiontF1 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviF1<- revcomF1[1:12]
reviF1 <- gsub("\n", "", reviF1)

reviF1

framet2 <- data.frame(
  Name = namerF1, 
  Date = daterevF1, 
  IndividualRating = indiF1, 
  Review = reviF1
)
framet2

framet6<- bind_rows(framet,framet2)
framet6
write.csv(framet6, file = "ReviewsPRODUCT6.csv")
```
SEVENT
```{r}
#product1 
#Part one 13 reviews
urlF <- "https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=four_star&pageNumber=1&formatType=current_format&reviewerType=avp_only_reviews&sortBy=recent"

sessiontF <- bow(urlF, user_agent = "Educational Purposes")
sessiontF


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontF <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_srt/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=four_star&pageNumber=1&formatType=current_format&reviewerType=avp_only_reviews&sortBy=recent")

#name of reviewr

namerevF <- sessiontF %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerF<- namerevF[1:13]
namerF

#date of review
dateF <- sessiontF %>%
  html_nodes("span.review-date") %>%
  html_text()
dateF
daterevF <- dateF[1:13]
daterevF


#individual rating
rateindiF <- sessiontF %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiF<- rateindiF[1:13]
indiF


#Review comment 
revcomF <- sessiontF %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviF<- revcomF[1:13]
reviF <- gsub("\n", "", reviF)
reviF

framet7 <- data.frame(
  Name = namerF, 
  Date = daterevF, 
  IndividualRating = indiF, 
  Review = reviF
)
framet7
#product 12 reviews

#Part two 12 reviews
urlF2 <- "https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful"

sessiontF2 <- bow(urlF2, user_agent = "Educational Purposes")
sessiontF2


sessiontF2 <- session("https://www.amazon.com.au/product-reviews/B084TNSDHN/ref=cm_cr_arp_d_viewopt_rvwer/358-8254970-8794523?pd_rd_w=KeGty&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=P3F3GQJHZ7WCD2Y0ZGF2&pd_rd_wg=Wek4F&pd_rd_r=62d0ea19-08ae-4795-b3f8-c2bbeaf43ea9&pd_rd_i=B084TNSDHN&filterByStar=five_star&pageNumber=1&formatType=current_format&reviewerType=all_reviews&sortBy=helpful")

#name of reviewr

namerevF2 <- sessiontF2 %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerF2<- namerevF2[1:12]
namerF2

#date of review
dateF2 <- sessiontF2 %>%
  html_nodes("span.review-date") %>%
  html_text()
dateF2
daterevF2 <- dateF2[1:12]
daterevF2


#individual rating
rateindiF2 <- sessiontF2 %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiF2<- rateindiF2[1:12]
indiF2


#Review comment 
revcomF2 <- sessiontF2 %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviF2<- revcomF2[1:12]
reviF2 <- gsub("\n", "", reviF2)

reviF2

framet72 <- data.frame(
  Name = namerF2, 
  Date = daterevF2, 
  IndividualRating = indiF2, 
  Review = reviF2
)
framet72

framet7_ <- bind_rows(framet7,framet72)
framet7_
write.csv(framet7_, file = "ReviewsPRODUCT7.csv")
```
EIGHT---
```{r}
#product8 

urlG <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1"

sessiontG <- bow(urlG, user_agent = "Educational Purposes")
sessiontG


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontG <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1")

#name of reviewr

namerevG <- sessiontG %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerG<- namerevG[1:12]
namerG

#date of review
dateG <- sessiontG %>%
  html_nodes("span.review-date") %>%
  html_text()
dateG
daterevG <- dateG[1:12]
daterevG


#individual rating
rateindiG <- sessiontG %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiG<- rateindiG[1:12]
indiG


#Review comment 
revcomG <- sessiontG %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviG<- revcomG[1:12]
reviG <- gsub("\n", "", reviG)
reviG

framet8 <- data.frame(
  Name = namerG, 
  Date = daterevG, 
  IndividualRating = indiG, 
  Review = reviG
)
framet8

#part two for 12 reviews

urG <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=positive&pageNumber=1"

sessionG <- bow(urG, user_agent = "Educational Purposes")
sessionG


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessionG <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewopt_sr/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=positive&pageNumber=1")

#name of reviewr

namereG <- sessionG %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

nameG<- namereG[1:13]
nameG

#date of review
datG <- sessionG %>%
  html_nodes("span.review-date") %>%
  html_text()
datG
datereG <- datG[1:13]
datereG


#individual rating
rateindG <- sessionG %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indG<- rateindG[1:13]
indG


#Review comment 
revcoG <- sessionG %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revG<- revcoG[1:13]
revG <- gsub("\n", "", revG)
revG

framet82 <- data.frame(
  Name = nameG, 
  Date = datereG, 
  IndividualRating = indG, 
  Review = revG
)
framet82
framet8_ <- bind_rows(framet8,framet82)
framet8_
write.csv(framet8_, file = "ReviewPRODUCT8.csv")
```
NINETH
```{r}
#product9

urlH <- "https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewpnt_rgt/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1"

sessiontH <- bow(urlH, user_agent = "Educational Purposes")
sessiontH


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontH <- session("https://www.amazon.com.au/product-reviews/B085G63QHT/ref=cm_cr_arp_d_viewpnt_rgt/358-8254970-8794523?pd_rd_w=nqMzK&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=MC2TYYP6DMVRAQZEWADY&pd_rd_wg=15aLU&pd_rd_r=c3604fac-49c7-4ff3-ab50-1c14e518d84d&pd_rd_i=B085G63QHT&filterByStar=critical&pageNumber=1")

#name of reviewr

namerevH <- sessiontH %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerH<- namerevH[1:25]
namerH

#date of review
dateH <- sessiontH %>%
  html_nodes("span.review-date") %>%
  html_text()
dateH
daterevH <- dateH[1:25]
daterevH


#individual rating
rateindiH <- sessiontH %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiH<- rateindiH[1:25]
indiH


#Review comment 
revcomH <- sessiontH %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviH<- revcomH[1:25]
reviH <- gsub("\n", "", reviH)
reviH

framet9 <- data.frame(
  Name = namerH, 
  Date = daterevH, 
  IndividualRating = indiH, 
  Review = reviH
)
framet9

write.csv(framet9, file = "100_PRODUCT9.csv")
```
TENTH
```{r}
#product1 

urle <- "https://www.amazon.com.au/product-reviews/B09B8YP8KY/ref=cm_cr_arp_d_viewpnt_lft/358-8254970-8794523?pd_rd_w=H67GR&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=3AKYM9QPH4FPGV2WWTV0&pd_rd_wg=cTVuK&pd_rd_r=68ad7cf9-3866-41d7-92f8-5bd39efe3eba&pd_rd_i=B09B8YP8KY&filterByStar=positive&pageNumber=1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont



sessiont <- session("https://www.amazon.com.au/product-reviews/B09B8YP8KY/ref=cm_cr_arp_d_viewpnt_lft/358-8254970-8794523?pd_rd_w=H67GR&content-id=amzn1.sym.26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_p=26572115-17fb-4b97-b3b1-43c572bafd8f&pf_rd_r=3AKYM9QPH4FPGV2WWTV0&pd_rd_wg=cTVuK&pd_rd_r=68ad7cf9-3866-41d7-92f8-5bd39efe3eba&pd_rd_i=B09B8YP8KY&filterByStar=positive&pageNumber=1")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1


write.csv(framet1, file = "ReviewPRODUCT10.csv")
```

ROWBIND
```{r} 
products<- bind_rows(framet1,framet9, framet8_,framet7_, framet6_, framet5_, framet4_, framet23_,frametA, framet1)
products
```
CSV

```{r} 
write.csv(products, file = "ProductReviews.csv")
```




```{r}
library(rvest)
library(stringr)
library(httr2) 
library(dplyr)


          session1p <- session("https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1708845383&ref=sr_pg_1")
          session1p
```


```{r}
name1 <- session1p %>%
  html_nodes("h2") %>%
  html_text()

one1<- name1[1:50]
one1

price1 <- session1p %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price1<- str_extract(price1[1:50], "\\$[0-9.]+")
# Print or use the first price
print(first_price1)


rating1<- session1p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three1<- rating1[1:50]
three1

review1 <- session1p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four1<- review1[1:50]
four1
```


```{r}
frame11 <- data.frame(
  Name = one1, 
  Price = first_price1, 
  Rating = three1, 
  Reviews = four1
)
frame11
```


```{r}
url2p <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1708845383&ref=sr_pg_1"

session2p <- bow(url2p, user_agent = "Educational Purposes")
session2p


```


```{r}
library(rvest)
library(stringr) 
library(httr2)


session2p <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk") 

```


```{r}

name2p <- session2p %>%
  html_nodes("h2") %>%
  html_text()

one2p<- name2p[1:48]
one2p

price2p <- session2p %>%
  html_nodes("span.a-price") %>%
  html_text()


first_price2p <- str_extract(price2p[1:48], "\\$[0-9.]+")

# 
print(first_price2p)


rating2p <- session2p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three2p<- rating2p[1:48]
three2p

review2p <- session2p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four2p<- review2p[1:48]
four2p

frame2p <- data.frame(
  Name = one2p, 
  Price = first_price2p, 
  Rating = three2p, 
  Reviews = four2p
)
frame2p
```



```{r}
url3p <- "https://www.amazon.com/s?k=gaming+hats&_encoding=UTF8&content-id=amzn1.sym.09483392-9ac6-434a-a3d7-39d83662f54a&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=OBZiU&pd_rd_wg=PaoPW&pf_rd_p=09483392-9ac6-434a-a3d7-39d83662f54a&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk"

session3p <- bow(url3, user_agent = "Educational Purposes")
session3p


library(rvest)
library(stringr)
library(httr2)
library(httr) 


session3p <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

```


```{r}
name3p<- session3p %>%
  html_nodes("h2") %>%
  html_text()

one3p<- name3p[1:2]
one3p

price3p <- session3p %>%
  html_nodes("span.a-price") %>%
  html_text()

# 
first_price3p <- str_extract(price3p[1:2], "\\$[0-9.]+")

# 
print(first_price3p)


rating3p <- session3p %>%
  html_nodes("span.a-size-base.s-underline-text") %>%
  html_text()

three3p<- rating3p[1:2]
three3p

review3p <- session3p %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

four3p<- review3p[1:2]
four3p

frame3p <- data.frame(
  Name = one3p, 
  Price = first_price3p, 
  Rating = three3p, 
  Reviews = four3p
)
frame3p
```

```{r}
products12<- bind_rows(frame1, frame2, frame3,frame11, frame2p, frame3p)
products12
```

```{r}
write.csv(products12,file = "ProductsReview200.csv")





Get the 25 Reviews each for 10 product. 
FIRST PRODUCT
```{r}
#product1 

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiont <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1

write.csv(framet1, file = "100_PRODUCT1.csv")
```
SECOND--------------------------
```{r}
#product2

urlA <- "https://www.amazon.com/Kasa-Smart-Security-Detection-KC410S/dp/B08ZXJJTYJ/ref=pd_bxgy_img_d_sccl_1/147-1768349-8840755?pd_rd_w=ARzFU&content-id=amzn1.sym.2b132e63-5dcd-4ba1-be9f-9e044543d59f&pf_rd_p=2b132e63-5dcd-4ba1-be9f-9e044543d59f&pf_rd_r=40XCD9QEVQ2J7CCJ61KG&pd_rd_wg=Rim0n&pd_rd_r=0f2d8bce-8434-4f79-ba3d-7b4fa09d3006&pd_rd_i=B08ZXJJTYJ&th=1"

session <- bow(urlA, user_agent = "Educational Purposes")
session


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontA <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerevA <- sessiontA %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerA<- namerevA[1:25]
namerA

#date of review
dateA <- sessiontA %>%
  html_nodes("span.review-date") %>%
  html_text()
dateA
daterevA <- date[1:25]
daterevA


#individual rating
rateindiA <- sessiontA %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiA<- rateindiA[1:25]
indiA


#Review comment 
revcomA <- sessiontA %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviA<- revcomA[1:25]
reviA <- gsub("\n", "", revi)
reviA

framet2 <- data.frame(
  Name = namerA, 
  Date = daterevA, 
  IndividualRating = indiA, 
  Review = reviA
)
framet2

write.csv(framet1, file = "100_PRODUCT2.csv")
```
THIRD----
```{r}

urlB <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiontB <- bow(urlB, user_agent = "Educational Purposes")
sessiontB

sessiontB <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerevB <- sessiontB %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerB<- namerevB[1:25]
namerB

#date of review
dateB <- sessiontB %>%
  html_nodes("span.review-date") %>%
  html_text()
dateB
daterevB<- dateB[1:25]
daterevB


#individual rating
rateindiB <- sessiontB %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiB<- rateindiB[1:25]
indiB


#Review comment 
revcomB <- sessiontB %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviB<- revcomB[1:25]
reviB<- gsub("\n", "", reviB)
reviB

framet1 <- data.frame(
  Name = namerB, 
  Date = daterevB, 
  IndividualRating = indiB, 
  Review = reviB
)
framet1

write.csv(framet1, file = "100_PRODUCT3.csv")
```
FOURTH
```{r}
library(rvest)
library(dplyr)
library(httr2)
library(httr)
library(purrr)


urlC <- "https://www.amazon.com/product-reviews/B086PKMZ21/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar"

sessiontC <- bow(urlC, user_agent = "Educational Purposes")

sessiontC <- session("https://www.amazon.com/product-reviews/B086PKMZ21/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")
#name of reviewer
namerevC <- sessiontC %>%
  make_request(urlC) %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerC <- namerevC[1:25]

#date of review
dateC <- sessiontC %>%
  make_request(urlC) %>%
  html_nodes("span.review-date") %>%
  html_text()

daterevC <- dateC[1:25]

#individual rating
rateindiC <- sessiontC %>%
  make_request(urlC) %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiC <- rateindiC[1:25]

#Review comment 
revcomC <- sessiontC %>%
  make_request(urlC) %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviC <- revcomC[1:25]
reviC <- gsub("\n", "", reviC)

framet1 <- data.frame(
  Name = namerC, 
  Date = daterevC, 
  IndividualRating = indiC, 
  Review = reviC
)
framet1

write.csv(framet1, file = "100_PRODUCT4.csv")


```

FIFTH
```{r}
#product1 

urlD <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiontD <- bow(urlD, user_agent = "Educational Purposes")
sessiontD


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontD <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerevD <- sessiontD %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerD<- namerevD[1:25]
namerD

#date of review
dateD <- sessiontD %>%
  html_nodes("span.review-date") %>%
  html_text()
dateD
daterevD <- dateD[1:25]
daterevD


#individual rating
rateindiD <- sessiontD %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiD<- rateindiD[1:25]
indiD


#Review comment 
revcomD <- sessiontD %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviD<- revcomD[1:25]
reviD <- gsub("\n", "", revi)
reviD

framet5 <- data.frame(
  Name = namerD, 
  Date = daterevD, 
  IndividualRating = indiD, 
  Review = reviD
)
frame5

write.csv(framet1, file = "100_PRODUCT5.csv")
```
SIXTH
```{r}
#product1 

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiontE <- bow(urle, user_agent = "Educational Purposes")
sessiontE


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiontE <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerevE <- sessiontE %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namerE<- namerevE[1:25]
namerE

#date of review
dateE <- sessiontE %>%
  html_nodes("span.review-date") %>%
  html_text()
dateE
daterevE <- dateE[1:25]
daterevE


#individual rating
rateindiE <- sessiontE %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indiE<- rateindiE[1:25]
indiE


#Review comment 
revcomE <- sessiontE %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

reviE<- revcomE[1:25]
reviE <- gsub("\n", "", revi)
reviE

framet6 <- data.frame(
  Name = namerE, 
  Date = daterevE, 
  IndividualRating = indiE, 
  Review = reviE
)
framet6

write.csv(framet1, file = "100_PRODUCT6.csv")
```

```{r}
#product1 

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiont <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1

write.csv(framet1, file = "100_PRODUCT7.csv")
```

```{r}
#product1 

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiont <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1

write.csv(framet1, file = "100_PRODUCT8.csv")
```

```{r}
#product1 

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiont <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()

revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1

write.csv(framet1, file = "ReviewPRODUCT9.csv")
```

```{r}
#product10

urle <- "https://www.amazon.com/s?k=video+gaming&page=2&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&qid=1707404161&ref=sr_pg_1"

sessiont <- bow(urle, user_agent = "Educational Purposes")
sessiont


library(rvest)
library(stringr)
library(httr2)
library(httr) 


sessiont <- session("https://www.amazon.com/s?k=video+gaming&_encoding=UTF8&content-id=amzn1.sym.4b335ede-a344-46a5-af28-95a1242a7034&pd_rd_r=d6faa99d-7b4f-4f66-ba1b-51efdc7ad720&pd_rd_w=ZXfjw&pd_rd_wg=PaoPW&pf_rd_p=4b335ede-a344-46a5-af28-95a1242a7034&pf_rd_r=Y73JSEQDQKY4X4KXWZNR&ref=pd_gw_unk")

#name of reviewr

namerev <- sessiont %>%
  html_nodes("span.a-profile-name") %>%
  html_text()

namer<- namerev[1:25]
namer

#date of review
date <- sessiont %>%
  html_nodes("span.review-date") %>%
  html_text()
date
daterev <- date[1:25]
daterev


#individual rating
rateindi <- sessiont %>%
  html_nodes("span.a-icon-alt") %>%
  html_text()

indi<- rateindi[1:25]
indi


#Review comment 
revcom <- sessiont %>%
  html_nodes("span.a-size-base.review-text.review-text-content") %>%
  html_text()


revi<- revcom[1:25]
revi <- gsub("\n", "", revi)
revi

framet1 <- data.frame(
  Name = namer, 
  Date = daterev, 
  IndividualRating = indi, 
  Review = revi
)
framet1

write.csv(framet1, file = "ReviewPRODUCT10.csv")
```



