---
title: "PracticalExam"
author: "Reysha Marie S. Salinas"
date: "2024-03-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


A. Load the built-in warpbreaks dataset.
```{r}
data("warpbreaks") 
warpbreaks
```

1. Find out, in a single command, which columns of warpbreaks are either numeric or
integer. What are the data types of each column?
```{r}
datatype <- sapply (warpbreaks, function(x) paste(class (x), collapse = "/"))
datatype
  
  #The breaks column is a double data type. 
  #The wool column is a factor data type. 
  #The tension column is a factor data type.
```

2. How many observations does it have?
```{r}
observation <- nrow(warpbreaks)
observation

#There are 54 observation in warpbreaks data set.
```

3. Is numeric a natural data type for the columns which are stored as such? Convert to
integer when necessary.
```{r}
warpbreaks$breaks <- as.integer(warpbreaks$breaks)
warpbreaks$breaks


```

4. Error messages in R sometimes report the underlying type of an object rather than the
user-level class. Derive from the following code and error message what the
underlying type. Explain what is the error all about. Do not just copy the error
message that was displayed.
```{r} 

#rete<-("rey")
#retw
#Error: object 'retw' not found

#The error is all about object name can't find, because retw object name is not use.
```


B. Load the exampleFile.txt
```{r}
library(readr)
path <- ("exampleFile.txt")
```

1. Read the complete file using readLines.
```{r}
readFile <- readLines(path)
readFile
```

2. Separate the vector of lines into a vector containing comments and a vector
containing the data. Hint: use grepl.
```{r}
comments <- readFile[grepl("^//", readFile)]
comments

dateLine <- readFile[!grepl("^//", readFile)]
dateLine
```

3. Extract the date from the first comment line and display on the screen “It was created
data.”
```{r}
date <- "21 May 2013" 
cat("It was created data:", date,"\n")
```

4. Read the data into a matrix as follows.
a. Split the character vectors in the vector containing data lines by semicolon (;)
using strsplit.
```{r}
split_data <- strsplit(dateLine, ";")
split_data
```

b. Find the maximum number of fields retrieved by split. Append rows that are
shorter with NA's.
```{r}
max_fields <- max(sapply(split_data, length))
max_fields 

rowappend <- lapply(split_data, function(x) c(x, rep(NA, max_fields - length(x)))) 
rowappend
          
```

c. Use unlist and matrix to transform the data to row-column format.
```{r}
undata <- unlist(rowappend) 

datamatrix <- matrix(undata, ncol = 4, nrow= 3)
datamatrix
```

d. From comment lines 2-4, extract the names of the fields. Set these as
colnames for the matrix you just created.
```{r}
field_names <- comments[2:4]
field_names1 <- gsub("//", "", field_names) 
field_names1
rownames(datamatrix) <- field_names1
print(datamatrix)
```
